Intrinsic Verification of Parsers and Formal Grammar Theory in Dependent Lambek Calculus

### 2025-03-25 paper/paper.tex
capitalize cubical

We use dependent polynomials functors on sets as these are guaranteed
to have initial algebras. Further, these initial algebras are readily
constructed in our Agda implementation as an inductive type of $IW$
trees which are already available in the cubical library of Agda
\cite{The_Agda_Community_Cubical_Agda_Library_2024}.  Then an element $F \in \sem{X \to
  \SPF\,X}\gamma$ is an $\sem{X}\gamma$-indexed family of polynomial
functors from $\sem{X}\gamma\times \Sigma^*$ to $\Sigma^*$, and taking
the product of these constructs a polynomial functor from
$\sem{X}\gamma\times \Sigma^*$ to itself. Then $\sem{\mu\,F}\gamma$ is
defined to be the initial algebra of this functor, and the initial
algebra structure is used to interpret $\roll, \fold$ and the
corresponding axioms.

>>>>

We use dependent polynomials functors on sets as these are guaranteed
to have initial algebras. Further, these initial algebras are readily
constructed in our Agda implementation as an inductive type of $IW$
trees which are already available in the Cubical library of Agda
\cite{The_Agda_Community_Cubical_Agda_Library_2024}.  Then an element $F \in \sem{X \to
  \SPF\,X}\gamma$ is an $\sem{X}\gamma$-indexed family of polynomial
functors from $\sem{X}\gamma\times \Sigma^*$ to $\Sigma^*$, and taking
the product of these constructs a polynomial functor from
$\sem{X}\gamma\times \Sigma^*$ to itself. Then $\sem{\mu\,F}\gamma$ is
defined to be the initial algebra of this functor, and the initial
algebra structure is used to interpret $\roll, \fold$ and the
corresponding axioms.
